---
title: "Adverse Event Counting Methods"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Adverse Event Counting Methods}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Setup

```{r setup}
# install.packages("gtreg")
library(gtreg)
```

# Overview

Reporting of adverse events to regulatory agencies typically employs both 
standardized terminology and specific counting methods for adverse events. 

# Standardized Terminology

Providing standardized terminology is not in the scope of this package. Standardized
terminology adheres to a hierarchy of terms from specific to general, as discussed
in the [MedDRA Hierarchy](https://www.meddra.org/how-to-use/basics/hierarchy) 
documentation. In {gtreg}, we facilitate reporting of a single term 
(i.e., `ae`, or adverse event), or a lower level term within a higher level term 
(i.e., `ae` within `soc`, system organ class). 

# Example Data

Data is typically recording in a long format with multiple rows per subject. 
Events can be reported over time, where both multiple time points per subject and 
multiple events per time point are possible. It is possible that grade of the
event is missing.

```{r create-data}
dat <- tibble::tribble(
    ~subject, ~visit,  ~soc, ~ae, ~grade,
    # Subject 1 ----------------------------------------------------------------
    "001", 1, "Eye disorders", "Eye irritation", 1,
    "001", 1, "Gastrointestinal disorders", "Difficult digestion", NA,
    "001", 2, "Eye disorders", "Eye irritation", 1,
    "001", 3, "Eye disorders", "Eye irritation", 2,
    "001", 4, "Eye disorders", "Vision blurred", 2,
    # Subject 2 ----------------------------------------------------------------
    "002", 1, "Gastrointestinal disorders", "Difficult digestion", 2,
    "002", 1, "Gastrointestinal disorders", "Reflux", 2,
    "002", 2, "Eye disorders", "Vision blurred", 2,
    "002", 2, "Gastrointestinal disorders", "Reflux", 2,
    "002", 3, "Gastrointestinal disorders", "Reflux", NA
  )
```

```{r print-data}
dat
```

# Challenges Addressed

Study participants without adverse events are absent from the adverse event 
raw data table. Furthermore,study participants may have multiple
adverse events, often with different severity grades.

These two features pose difficulties to computing the percentage of participants
who experience a specific adverse event. 

1. In the numerator, we want to count need to make sure that we do not double count the same AE within
each participant, and in the denominator we need to make sure we include all patients 
in the treatment arm (not just those who experience an AE). 
These challenges are amplified when AE terms need to roll up into system organ class
summaries.
Functions in {gtreg} address these problems (among others) by implementing industry
recommended approaches. 
For further reading, the PHUSE white paper regarding
[Analysis and Displays Associated with Adverse events](https://phuse.s3.eu-central-1.amazonaws.com/Deliverables/Standard+Analyses+and+Code+Sharing/Analyses+and+Displays+Associated+with+Adverse+Events+Focus+on+Adverse+Events+in+Phase+2-4+Clinical+Trials+and+Integrated+Summary.pdf)
provides an excellent summary of such standards.

# Counting All Events

To count _all_ instances of any event, utilize `tbl_ae_count`.

```{r count-all}
dat %>% 
  tbl_ae_count(
    ae = ae,
    soc = soc,
    by = grade
  ) %>% 
  modify_ae_header(all_ae_cols() ~ "**Grade {by}**") %>% 
  add_overall() %>% 
  bold_labels()
```

In this case, we have two subjects which experienced a total of 5 eye disorders and 4
gastrointestinal disorders over the course of multiple time points. The only statistic 
allowed in `tbl_ae_count()` is `n`.

# Counting By Highest Grade

Rather than counting all events, it is typical in regulatory reporting to count
one event per subject by the highest grade experienced. To count the highest grade 
per subject, utilize `tbl_ae()`. 

The input `by` variable can be numeric (e.g., grade 1, 2, 3) or factor
(e.g. attribution unlikely, possible, definite). In the respective cases,
the highest value observed would be according to numeric order or factor
level order, with missing values considered as the lowest level.

When counting by highest grade, the count reported in any cell cannot exceed the 
number of subjects. These methods apply to both the individual adverse events and
the system organ class.

## Counts Only

```{r count-max-1}
dat %>% 
  tbl_ae(
    id = subject,
    ae = ae,
    soc = soc,
    by = grade,
    statistic = "{n}"
  ) %>% 
  modify_ae_header(all_ae_cols() ~ "**Grade {by}**") %>% 
  add_overall() %>% 
  bold_labels()
```

### Adverse Events

* Subject `001` experienced two instances of grade 1 eye irritation and one instance
of grade 2 eye irritation. The maximum grade experienced of eye irritation experienced is 2,
resulting in a count of `1` for eye irritation.

* Subject `001` and Subject `002` both experienced grade 2 vision blurred, resulting
in a count of `2` of vision blurred.

* Subject `002` experienced two instances of grade 2 reflux and one instance of 
reflux with unknown grade; in a count of `1` for grade 2 reflux.


### System Organ Class

_Eye disorders_

 + Subject `001` contributes 1 count to grade 2 eye irritation; together, subject `001` and `002` 
contribute 2 counts to grade 2 vision blurred. 

 + 2 subjects experienced a grade 2 eye disorder.
 
 + 2 subjects overall experienced an eye disorder.

_Gastrointestinal disorders_

 + Subject `001` experienced difficult digestion of unknown grade, and contributes
 a count of 1 to unknown grade gastrointestinal disorder.
 
 + Subject `002` experienced both grade 2 difficult digestion and grade 2 reflux, and 
 contributes a count of 1 to grade 2 gastrointestinal disorders.

 + 2 subjects overall experienced a gastrointestinal disorder.


## Counts With Percents

The default statistic reported for `tbl_ae()` is `n (%)`. The percent represents
the percent of all subjects present in the data.

```{r count-max-2}
dat %>% 
  tbl_ae(
    id = subject,
    ae = ae,
    soc = soc,
    by = grade
  ) %>% 
  modify_ae_header(all_ae_cols() ~ "**Grade {by}**") %>%
  modify_ae_spanning_header(all_ae_cols() ~ "**N = {N}**") %>% 
  add_overall() %>% 
  bold_labels()
```

In adverse event reporting, it is common that not all subjects experience
an adverse event, and hence are not included in the event reporting data set. 
For example, suppose there were 3 subjects of interest in this study, but 
subject `003` did not experience an adverse event. In order to get the correct 
subject denominator in this case, supply `tbl_ae()` with `id_df`, a data frame 
containing all subject ids.


```{r count-max-3}
dat %>% 
  tbl_ae(
    id = subject,
    id_df = tibble::tibble(subject = c("001", "002", "003")),
    ae = ae,
    soc = soc,
    by = grade
  ) %>% 
  modify_ae_header(all_ae_cols() ~ "**Grade {by}**") %>% 
  modify_ae_spanning_header(all_ae_cols() ~ "**N = {N}**") %>% 
  add_overall() %>% 
  bold_labels()
```


