---
title: "Mock TLFs"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Mock TLFs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, warning=FALSE, message=FALSE}
library(gtreg)
library(tidyverse)
```

# Overview

Mock tables are tables with generic `xx` place holders for numeric
values.  Mock tables can be generated by: 

1. Create dummy data or use your own data.

2. Pass the data to your function of choice.

3. Overwrite the statistic(s) shown to a fixed character string by implementing
the `style_xxx()` function in the `digits` argument.

# `tbl_ae()` 


## `tbl_ae()` uniform

Here, we specify the `digits` argument to uniformly apply to all summary
statistics in the table; in this case this is both `n` and `%`.

```{r}
dat_ae %>% 
 tbl_ae(
        id = id,
        ae = ae,
        soc = soc,
        by = grade,
        digits = purrr::partial(style_xxx, width = 2)
      ) %>%
      modify_header(all_ae_cols() ~ "**Grade {by}**") %>%
      modify_spanning_header(all_ae_cols() ~ "**N = xx**")
```

# `tbl_ae()` custom

If you want custom formatting that differ between `n` and `%`, specify
the `digits` argument with a `list`.

```{r}
dat_ae %>% 
 tbl_ae(
        id = id,
        ae = ae,
        soc = soc,
        by = grade,
        digits =
          list(
            purrr::partial(style_xxx, width = 2), #  n
            purrr::partial(style_xxx, width = 4, digits = 1) # %
            )
      ) %>%
      modify_header(all_ae_cols() ~ "**Grade {by}**") %>%
      modify_spanning_header(all_ae_cols() ~ "**N = xx**")
```


# `tbl_reg_summary()` 


## `tbl_reg_summary()` uniform

Here, we specify the `digits` argument to uniformly apply to all summary
statistics in the table; in this case this is both `n` and `%`.

```{r}
df_patient_characteristics %>%
      select(marker, trt) %>%
      tbl_reg_summary(
        digits =
          list(
            all_continuous2() ~ purrr::partial(style_xxx, width = 2),
            all_categorical() ~ purrr::partial(style_xxx, width = 2)
          )
      ) %>%
      modify_header(stat_0 ~ "**N = xx**")
```

# `tbl_reg_summary()` custom

If you want custom formatting that differ between `n` and `%`, specify
the `digits` argument with a `list`.

```{r}
df_patient_characteristics %>%
      select(marker, trt) %>%
      tbl_reg_summary(
        digits =
          list(
            all_categorical() ~ list(
              purrr::partial(style_xxx, width = 2),             # n 
              purrr::partial(style_xxx, width = 4, digits = 1)  # %
              ),    
            all_continuous2() ~ list(
              purrr::partial(style_xxx, width = 2),             # N
              purrr::partial(style_xxx, width = 4, digits = 1), # Mean
              purrr::partial(style_xxx, width = 4, digits = 1), # SD
              purrr::partial(style_xxx, width = 2),             # Median
              purrr::partial(style_xxx, width = 2),             # IQR
              purrr::partial(style_xxx, width = 2),             # Range
              purrr::partial(style_xxx, width = 2)              # N missing
          ))) %>%
      modify_header(stat_0 ~ "**N = xx**")
```

